%% start of file `template.tex'.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\name{Robert}{Kozikowski}
\social[linkedin]{kozikow}                % optional, remove the line if not wanted
\phone[mobile]{+44 7857773182}                    % optional, remove the line if not wanted
\email{r.kozikowski@gmail.com}                      % optional, remove the line if not wanted
\homepage{kozikow.wordpress.com}                % optional, remove the line if not wanted

\definecolor{CadetBlue}{RGB}{58,128,179}
% color hyperlinks
\AtBeginDocument{
    \hypersetup{colorlinks,urlcolor=CadetBlue}
}

%\extrainfo{\url{http://markliu.me}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Experience}

\cventry{Jan 2014 - Now}{Google}{Software Engineer}{London}{Java, Python}{
Google Search
\begin{itemize}%
\item
  Logs and data analysis - Collected, processed and analyzed petabytes of data.
  Built continuous data processing pipelines spanning thousands LOC and ingesting
  30+ TB per day. Created dashboards and analysis tools. Used stats and ML.
\item Performance and reliability - Improved the android search app latency. Reduced the memory,
  battery and bandwidth footprint. Fixed reliability problems. Designed and implemented
  APIs with focus on efficiency, concurrency, and robustness.
\end{itemize}
}

\cventry{2013}{Contracting and various jobs}{}{}{}{
  Created a one person consulatancy company and worked on a various jobs including:
  \begin{itemize}
  \item
    Distributed logs analysis SaaS on amazon web services using scala.
  \item
    Optimizing the android application performance.
  \end{itemize}
}

\cventry{Summer 2012}{Google}{Intern}{Dublin}{Python, JavaScript}{
End to end implementation of a web based data analysis tool, including frontend and backend.
}

\cventry{Summer 2011}{Microsoft}{Intern}{Headquarters}{C++}{
Added a performance focused feature to a distributed database used in the Bing search engine.
}

\section{Education}
\cventry{2009 - 2012}{BSc, Computer Science}{University of Warsaw}{}{}{}

\section{Technical proficiency}
\cvline{Languages}{Java, Python, C++, JavaScript, Scala.}
\cvline{Specializations}{Algorithms and data structures, android, performance and latency optimization, data analysis, statistics, machine learning.}

\section{Other}
\cvline{Programming Contests}{
  \httplink[81th place at Google Code Jam 2010]{code.google.com/codejam/contest/639102/scoreboard\#sp=61}, Bronze medal at Polish olympiad in informatics 2009, successes and many problems solved on ACP ICPC, TopCoder, Hackerrank, etc.}
\cvline{Publications}{Applications of algorithms in programming contests, ISBN 978-83-930856-3-7 (Co-author with Jacek Tomasiewicz).}
\cvline{Courses}{Machine learning on coursera.}

\end{document}
