%% start of file `template.tex'.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\name{Robert}{Kozikowski}
\social[linkedin]{kozikow}                % optional, remove the line if not wanted
\phone[mobile]{+44 7857773182}                    % optional, remove the line if not wanted
\email{r.kozikowski@gmail.com}                      % optional, remove the line if not wanted
\homepage{kozikow.wordpress.com}                % optional, remove the line if not wanted

\definecolor{CadetBlue}{RGB}{58,128,179}
% color hyperlinks
\AtBeginDocument{
    \hypersetup{colorlinks,urlcolor=CadetBlue}
}

%\extrainfo{\url{http://markliu.me}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Experience}

\cventry{Jan 2014 - Now}{Google}{Software Engineer}{London}{Java, Python}{
Android Google Search
\begin{itemize}%
\item
  Logs and data analysis - Collected, processed and analyzed petabytes of data.
  Built continuous data processing pipelines spanning thousands LOC and ingesting
  30+ TB per day. Created dashboards and analysis tools. Used stats and ML.
\item Performance and reliability - Improved the android app latency. Reduced the memory,
  battery and bandwidth footprint. Fixed reliability problems. Designed and implemented
  APIs with focus on efficiency, concurrency, and robustness.
\item Monitoring and alerting - Set up real time monitoring and alerting. Diagnosed and fixed many problems during on-call.
\end{itemize}
}

\cventry{End of 2013}{Contractor}{Sumo Logic}{Poland}{Scala}{
Moved back to Poland for personal reasons. AWS deployement of a distributed (100+ machines) logs analysis system developed in Scala.
}

\cventry{2012 - 2013}{Facebook}{Software Engineer}{London}{Java}{
Facebook Android App. Improving the mobile app infrastructure focusing on performance.
}

\cventry{Summer 2012}{Google}{Intern}{Dublin}{Python, JavaScript}{
End to end implementation of a web based data analysis tool, including frontend and backend.
}

\cventry{Summer 2011}{Microsoft}{Intern}{Headquarters}{C++}{
Added a performance focused feature to a distributed database used in the Bing search engine.
}

\section{Education}
\cventry{2009 - 2012}{BSc, Computer Science}{University of Warsaw}{}{}{}

\section{Proficiency out of 10}
\cvline{Languages}{Java 10, Python 7, C++ 7, JavaScript 6, Scala 6, many others <6.}
\cvline{Technologies}{Algorithms and data structures 10, performance and latency optimization 10, android 10, concurrency (in Java) 8, monitoring 7, data science 6, statistics and machine learning 6.}

\section{Other}
\cvline{Programming Contests}{
  \httplink[81th place at Google Code Jam 2010]{code.google.com/codejam/contest/639102/scoreboard\#sp=61}, Bronze medal at Polish olympiad in informatics 2009, successes and many problems solved on ACP ICPC, TopCoder, Hackerrank, etc.}
\cvline{Publications}{Applications of algorithms in programming contests, ISBN 978-83-930856-3-7 (Co-author with Jacek Tomasiewicz).}

\end{document}
